---
title: "Bootstrap"
author: "Matthew Johnson"
date: "November 9, 2017" 
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 5, fig.height = 4, echo = TRUE)
suppressMessages({
  library(tidyverse)
  library(boot)
})
```


```{r, Problem 1, Part A}
data("diamonds")
p <- qplot(clarity, price, data=diamonds, geom="boxplot") + stat_summary(fun.y=mean, colour="dark gray",
geom="point", size=4) + theme(axis.text.x=element_text(angle=45, hjust=1))
p
model <- lm(price~clarity, data=diamonds)
anova(model)
yhat <- fitted(model)
yhat
```
The values that are returning are the estimated mean of that data point given its clarity.

```{r Problem 1, Part B}
coefficients(model)
```
The intercept is the difference in group mean between the first level, which is called a intercept, and the rest of the levels' group means.

```{r, Problem 1, Part C}
(residuals(model))
```
I chose a positive number, 288.88536, and a negative number, -516.73707. What these numbers show is the difference between the sampled data point and the calculated mean for its group. 288 means that the sampled data point was $288 more than the group mean for the group it belonged to. The negative number shows just the opposite, $516 less than the group average for that sampled data point.

Problem 2, Part A
For Problem 2, we'll be using the Diamonds dataset that I have used in the previous question, which is a built in dataset with tidyverse. I'll be using different variables. I will be using the variable Cut against the variable Price. I'm looking to see the correlation between the cut of a diamond and the average price. We're going to be using a 98% confidence interval, meaning an alpha of 0.02.
```{r Problem 2, Part B}
p2 <- qplot(cut, price, data=diamonds, geom="boxplot") + stat_summary(fun.y=mean, colour="dark gray",
geom="point", size=4) #+ theme(axis.text.x=element_text(angle=45, hjust=1))
p2
```
Problem 2, Part C
 
```{r}
diff_means <- function(data, i) {
  data[i,] %>%
    group_by(cut) %>%
    summarise(m=mean(price)) %>%
    .[['m']] %>% # extract column named m
    diff %>% # take difference in
    `*`(-1) # same order as t.test
}

b <- diamonds %>%
  select(price, cut) %>%
  na.omit %>%
  boot(., statistic=diff_means, R=2000,
    parallel="multicore", ncpus=4) # dope

bCI <- boot.ci(b, conf=0.95, type="bca")
bCI
```
