## Lab 01: Introduction to Statistics and R

To compile this document in RStudio open the file and click knit in the toolbar.  In any other text editor, call rmarkdown::render() on this file's quoted filepath.  You may need to install the library named rmarkdown first.  Learn more about [Rmarkdown](http://rmarkdown.rstudio.com/lesson-1.html) and [knitr](https://yihui.name/knitr/).

1. R(Studio) has built in help files, try
?mean

2. Read in the dataframe from Lecture IntroStats slide 13/76 into a
 variable named email.

```{r}
url <- "https://roualdes.us/data/email.csv"
email <- read.csv(url)
```

3. Copy and paste all the code from Lecture IntroStats slide 13/76 -
23/76

```{r}
is.factor(email$number)
is.factor(email$spam)
is.numeric(email$spam)
head(email$spam)
is.factor(factor(email$spam))
is.numeric(email$num_char)
phat <- sum(email$spam)/length(email$spam)
phat == mean(email$spam)
```

4. Pick another numerically encoded, binary, categorical variable
from this dataset named email, and calculate the proportion two
ways.  Assuming this is a random sample of emails, interpret the
number in language that your grandmother could understand.
Hints: ?head; ?names; ?== or ?\`==\`

```{r}
sum(email$to_multiple)/length(email$to_multiple)
mean(email$to_multiple)
```

An estimate of the true population proportion of emails that are
directed to multiple recipients is about `r round(mean(email$to_multiple), 2)`%.

5. You can create regular sequences with :.  Use : to create a
regular sequence of non-zero integers less than 3921 and store it
into a variable named x.  Just for added difficulty later on, don't
start at 1.

Hint: one of these should work for you ?\`:\` # or ?:

```{r}
x <- 4:62
```

6. R uses square brakets [] for indexing vectors.  Extract the
first element of the variable you named x, by indexing it
with brackets.

Hint: ?\`[\` # or ?[

```{r}p
x[1]
```

7. Using the variable you unamed x, extract x-th elements from a
column of your choice from the dataframe named email.

```{r}
email$to_multiple[x]
```

8. Use a for loop to accomplish the same thing from 7.

```{r}
## if you are going to store these values, initialize the storage
## container first.  A good way to do this in R is
out <- rep(NA, length(x))
for (i in seq_along(x)) {
    out[i] <- email$to_multiple[x[i]]
}
## now, if any  values of out are still NA, we know we messed up
```

9. Pick a continuous, numerical variable from the dataframe email
and calculate the mean, median, and standard deviation.
For added challenge, try using dplyr::summarise.

Hint: library(tidyverse); ?dplyr::summarise

```{r}
## for more on dplyr read http://seananderson.ca/2014/09/13/dplyr-intro.html
library(dplyr)                          # or tidyverse
dplyr::summarise(email,
                 mn=mean(line_breaks),
                 mdn=median(line_breaks),
                 s=sd(line_breaks))
```

10. Using the dataframe email, make one of each type of plot -- don't
steal my plots, make your own.

```{r, fig.width=4, fig.height=4, fig.align="center"}
library(ggplot2)                        # or tidyverse
qplot(spam, data=email, geom="bar")
qplot(num_char, data=email, geom="histogram", bins=30)
qplot(factor(to_multiple), num_char, data=email, geom="boxplot")
qplot(num_char, line_breaks, data=email)
```