---
title: "Regression"
author: "Matthew Johnson"
date: "November 17, 2017" 
output: html_document
---

```{r}
knitr::opts_chunk$set(fig.width = 5, fig.height = 4, echo = TRUE)

suppressMessages({
  library(tidyverse)
  saltmarsh <- read.csv("C:/Programming/R stuff/saltmarsh.csv")
})
```

1. I chose the provided dataset at roualdes.us/data/saltmarsh.csv
    and I'm choosing the variables salt and biomass in an attempt
    to view any correlation between the amount of salt placed
    and the corresponding biomass that grew on it.

```{r, Part 2}
p <- qplot(salt, biomass, data = saltmarsh)
p + stat_smooth(method="lm", se=FALSE) # no standard error
R <- with(saltmarsh,
     cor(salt, biomass))
saltReg <- lm(biomass~salt, data = saltmarsh)
summary(saltReg)
```

3. The slope is -0.492 with a correlation of -0.647 and an intercept of 20.210.

4. My adjusted R-squared is .3921. Therefore, 39.21% of the variation in biomass
   is explained by the least squares line on salt.

5.
H0: B = 0;
H1: B != 0
alpha = 0.02
```{r}
confint(saltReg, level = 0.98)
```
6.
We are 98% confident when salt is 0, the amount of biomass is between 12.7 and 27.7 grams.
We can reject the null hypothesis because our salt interval does not contain the
null hypothesis.
When there is no salt in the puddles, the expected amount of biomass is between 12.7 and 27.7 grams.
Adding any amount of salt does not cause biomass to stay the same.