## 1. Load the dataset ape::carnivora.
## Hint: ?ape::carnivora

```{r}
library(ape)
data(carnivora)
```


## 2. Pick a numerical variable with missing data, names a variable
## that contains NAs.
## Hint: ?anyNA

```{r}
BW_has_NA <- is.na(carnivora$BW)
```


## 3. Calculate the number of observations in your chosen vector.
## Hints: ?is.na, ?`!` sum(c(TRUE, FALSE, TRUE)) == 2

```{r}
nm_of_obs <- sum(!BW_has_NA)
```


## 4. Why doesn't length work to count observations?  What's the
## difference between (the correct answer for) 3. and what length
## returns?

What is returning is "TRUE" for every NA listed, so when we're looking for observations, we're looking for NOT NA. When we not the vector, we get the inverse, which is the actual observations we're looking for.

## 5. Calculate mean/standard deviation/median/IQR by SuperFamily and
## then (separately) by Family for your chosen numerical variable.
## Hint: see SummariesByGroup examples

```{r}
(df <- dplyr::summarise(dplyr::group_by(carnivora, SuperFamily),
                        Mn=mean(BW, na.rm = TRUE),
                        StDev=sd(BW, na.rm = TRUE),
                        Med=median(BW, na.rm = TRUE),
                        IQR=IQR(BW, na.rm = TRUE)))
```


## 6. Make a box plot for your numerical variable by region.

```{r}
ggplot2::qplot(data=carnivora, SuperFamily, BW, geom="boxplot")
```


## 7. Plot your numerical variable by region as a scatter plot, then
## add the mean and standard errors (some other quantity we'll learn
## about later).
## Hint: ?ggplot2::stat_summary

## 8. Even if you don't fully understand the bars sticking out of the
## mean, can you see any major differences in terms of measure of
## center, measure of spread, and measure of skew between the plots in
## 6. and 7.?
